Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-16 manuscript/paper-tycho.tex
Imgs for paper/poster; minor code/paper tweaks
Clean code for parameter space grids
Update paper images; generate set of good images for poster
Organize code / notes for Tycho images

\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[iop, apj, numberedappendix]{emulateapj}

@@

% Customize figures/sizing for 2 column vs. manuscript printout
\usepackage{etoolbox}
\newtoggle{manuscript}
\toggletrue{manuscript}
%\togglefalse{manuscript}

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using a
model for particle transport with an exponentially cut-off injected electron
spectrum, we fit width measurements to model predictions in the loss-limited
and magnetic damping scenarios to obtain estimates on magnetic field strength
and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
and attempt to constrain damping through spectral variation downstream of the
forward shock and considering both radio and X-ray rim morphology.
%and the implications for future studies of young supernova remnant shocks.

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{ % TODO a temporary image
        \includegraphics[width=0.3\textwidth]{figures/radio-snr-inv.png}
    }{
        \plotone{figures/radio-snr-inv.png}
    }
    \caption{Radio image of Tycho's SNR at $1.375 \unit{GHz}$ with linear
    scaling.  Extraction regions (green) for joint radio and X-ray profile
    analysis overlay region selections for X-ray rim width analysis
    (Figure~\ref{fig:snr}). \label{fig:radio-snr}}
\end{figure}

@@

% Results: linchpin for damping model here
A loss-limited rim model (constant magnetic field $B_0$) cannot produce thin
radio rims.  Our model requires damping length $a_b \lesssim 0.1$ to produce a
plateau or thin rim in radio emission.  For regions with thin radio rims, the
best manually selected profiles have $B_0$ between $50$--$400 \muG$, neglecting
only Region N which could not be modeled simultaneously in both X-ray and radio
(Figure~\ref{fig:radio-prfs-meh}).  The damping length $a_b$ ranges between
$0.01$--$0.03$, or $2$--$7\arcsec$.  The radio plateaus in regions B, C, D are
compatible with damping lengths between $0.01$--$0.05$.  Continuous rises in
radio emission are best modeled with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300
\muG$.  Although damping lengths $a_b \gtrsim 0.1$ may not be physically
meaningful, such large values of $a_b$ yield practically constant magnetic
field behind the shock regardless.

% TODO what happens if \Bmin = 2 \muG?!

>>>>

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
\documentclass[iop, apj, numberedappendix]{emulateapj}

@@

% Customize figures/sizing for 2 column vs. manuscript printout
\usepackage{etoolbox}
\newtoggle{manuscript}
%\toggletrue{manuscript}
\togglefalse{manuscript}

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using a
model for particle transport with an exponentially cut-off injected electron
spectrum, we fit width measurements to model predictions in the loss-limited
and magnetic damping scenarios to obtain estimates on magnetic field strength
and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
and attempt to constrain damping by (1) measuring and modeling spectral variation
downstream of the forward shock, and (2) jointly modeling both radio and X-ray
rim morphology.
%and the implications for future studies of young supernova remnant shocks.

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.3\textwidth]{figures/radio-snr-inv.png}
    }{
        \plotone{figures/radio-snr-inv.png}
        %\plotone{figures/radio-snr.eps}
    }
    \caption{Radio image of Tycho's SNR at $1.375 \unit{GHz}$ with linear
    scaling.  Extraction regions (green) for joint radio and X-ray profile
    analysis overlay region selections for X-ray rim width analysis
    (Figure~\ref{fig:snr}). \label{fig:radio-snr}}
\end{figure}

@@

% Results: linchpin for damping model here
A loss-limited rim model (constant magnetic field $B_0$) cannot produce thin
radio rims.  Our model requires damping length $a_b \lesssim 0.1$ to produce a
plateau or thin rim in radio emission.  For regions with thin radio rims, the
best manually selected profiles have $B_0$ between $50$--$400 \muG$, neglecting
only Region N which could not be modeled simultaneously in both X-ray and radio
(Figure~\ref{fig:radio-prfs-meh}).  The damping length $a_b$ ranges between
$0.01$--$0.03$, or $2$--$7\arcsec$.  The radio plateaus in regions B, C, D are
compatible with damping lengths between $0.01$--$0.05$.  Continuous rises in
radio emission are best modeled with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300
\muG$.  Although damping lengths $a_b \gtrsim 0.1$ may not be physically
meaningful, such large values of $a_b$ yield practically constant magnetic
field behind the shock regardless.
Our results are also insensitive to the assumed value of $\Bmin$; only model
profiles with small magnetic fields ($B_0 \lesssim 100 \muG$) and/or small
damping length ($a_b < 0.01$) are affected if we take $\Bmin = 2 \muG$ rather
than $5 \muG$.
% TODO rewrite for clarity (!)
